\thetitle

### 2024-11-10 paper/paper.tex
Recolor graphs

Luminosity distance, $D_L$, is the apparent distance of an object based on the
measured luminosity. This does not take into account any movement of the
observed object between the time when the light was emitted and the light is
observed.

Measurements of Type Ia supernova provide magnitude and redshift. To derive the
luminosity distance from these measurements, we start by computing the relative
brightness. Magnitude $M$ is defined on a logarithmic scale where magnitude 1 has
100 times the brightness of magnitude 6. To convert magnitude to relative
brightness $B$, we use

\begin{equation}
  B = \frac{1}{\sqrt[5]{100}^{M - 1}}.
\end{equation}

@@

\begin{equation}
  B^{*} = B \frac{E_{\text{emit}}}{E_{\text{obs}}}.
\end{equation}

@@

\begin{equation}
\begin{aligned}
  B^{*} &= B \frac{\frac{hc}{\lambda_{\text{emit}}}}{\frac{hc}{\lambda_{\text{obs}}}} \\
        &= B \frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}}.
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  B^{*} &= B \frac{(1 + z)\lambda_{\text{emit}}}{\lambda_{\text{emit}}} \\
        &= B(1 + z).
\end{aligned}
\end{equation}

@@

where $d$ is the relative distance between the two objects.

@@

\begin{equation}
\begin{aligned}
  B^{*} = \pi \bigg(\frac{r}{d}\bigg)^2 \\
      d = r \sqrt{\frac{\pi}{B^*}}.
\end{aligned}
\end{equation}

Finally, since this equation has no specified units, we will need to find a calibration factor $k$. To beautify the equation, we can collect all constants (which includes $r$ since all Type Ia supernova have the same intrinsic brightness) into $k$. This gives

\begin{equation}
\begin{aligned}
  d &= r \sqrt{\frac{\pi}{\frac{1}{\sqrt[5]{100}^{M - 1}}(1 + z)}} \\
    &= \frac{k 10^\frac{M}{5}}{\sqrt{z + 1}}.
\end{aligned}
\end{equation}

@@

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/corrected_uncalibrated.png}
  \caption{Uncalibrated distance model using the corrected $B^*$ values for
  brightness.}
  \label{fig:corrected_uncalibrated}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/uncorrected_uncalibrated.png}
  \caption{Uncalibrated distance model using the uncorrected $B$ values for brightness.
  The deviation from linearity suggests that distant objects are
  farther away than expected due to an accelerated expansion rate.}
  \label{fig:uncorrected_uncalibrated}
\end{figure}

It's worth noting that previous studies use $B$ instead of $B*$. According to
\citet{betoule2014},

\begin{displayquote}
  Specifically, the distance estimator used in this analysis (and in most
  similar cosmological analyses) assumes that supernovae with identical color,
  shape and galactic environment have on average the same intrinsic luminosity
  for all redshifts.
\end{displayquote}

This leads to

\begin{equation}
  d_{\text{uncorrected}} = k 10^\frac{M}{5}
\end{equation}

which is displayed in Figure \ref{fig:uncorrected_uncalibrated}.

\section{Calibrated distance models}
\label{sec:disproof}

@@

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/both_calibrated_velocity_vs_distance.png}
  \caption{Calibrated distance model using both the corrected $B^*$ values as
  well as the uncorrected $B$ brightness values.}
  \label{fig:calibrated}
\end{figure}

\section{Next steps}
\label{sec:nextsteps}

Is my understanding of the literature correct? My understanding is that
existing models don't correct for the impact of redshift on the brightness of
distant objects, and models that use an accelerating expansion for the universe
are based on adding that correction back into the model.

If that's accurate, it would be interesting to repeat the computation of
cosmological constants. Is there evidence for acceleration or deceleration
for the expansion rate?

Find a bigger dataset. Use \citet{abbott2024} perhaps?

Is it necessary to figure out a hypothesis test? What would that even look
like?

>>>>

Luminosity distance $D_L$, is the apparent distance of an object based on the
observed luminisity, also known as the flux $F$.  This does not take into
account any movement of the observed object between the time when the light was
emitted and the light is observed. $D_L$ also does not take into account
redshift. We are instead interested in $D_{L^*}$, which is the distance based
on the luminosity corrected for redshift.

Measurements of Type Ia supernova provide magnitude and redshift. To derive the
luminosity distance from these measurements, we start by computing the flux
$L$. Magnitude $M$ is defined on a logarithmic scale where magnitude 1 has 100
times the brightness of magnitude 6, leading to

\begin{equation}
  F = \frac{1}{\sqrt[5]{100}^{M - 1}}.
\end{equation}

@@

\begin{equation}
  F^{*} = F \frac{E_{\text{emit}}}{E_{\text{obs}}}.
\end{equation}

@@

\begin{equation}
\begin{aligned}
  F^{*} &= F \frac{\frac{hc}{\lambda_{\text{emit}}}}{\frac{hc}{\lambda_{\text{obs}}}} \\
        &= F \frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}}.
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  F^{*} &= B \frac{(1 + z)\lambda_{\text{emit}}}{\lambda_{\text{emit}}} \\
        &= B(1 + z).
\end{aligned}
\end{equation}

To compute the corrected magnitue $M^*$, we can solve

\begin{equation}
\begin{aligned}
   F^* &= \frac{1}{\sqrt[5]{100}^{M^* - 1}} \\
   M^* &= M - \frac{\ln{(z + 1)}}{\ln{(\sqrt[5]{100})}}.
\end{aligned}
\end{equation}

@@

where $D$ is the relative distance between the two objects.

@@

\begin{equation*}
  F^{*} = \pi \bigg(\frac{r}{D}\bigg)^2
\end{equation*}

\begin{equation}
\label{eq:D*}
  D_{L^*} = r \sqrt{\frac{\pi}{F^*}}.
\end{equation}

Since this equation has no specified units, we will need to find a
calibration factor $k$. To beautify the equation, we can collect all constants
(which includes $r$ since all Type Ia supernova have the same intrinsic
brightness) into $k$. This gives

\begin{equation}
\begin{aligned}
  D_{L^*} &= r \sqrt{\frac{\pi}{\frac{1}{\sqrt[5]{100}^{M - 1}}(1 + z)}} \\
          &= \frac{k 10^\frac{M}{5}}{\sqrt{z + 1}}.
\end{aligned}
\end{equation}

@@

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/corrected_uncalibrated.png}
  \caption{Uncalibrated distance model using the corrected $F^*$ values for
  brightness. The data were obtained from \citet{betoule2014}.}
  \label{fig:corrected_uncalibrated}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/uncorrected_uncalibrated.png}
  \caption{Uncalibrated distance model using the uncorrected $F$ values for brightness.
  The deviation from linearity suggests that distant objects are
  farther away than expected due to an accelerated expansion rate.}
  \label{fig:uncorrected_uncalibrated}
\end{figure}

\section{Calibrated distance models}
\label{sec:calibrated}

@@

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/both_calibrated_velocity_vs_distance.png}
  \caption{Calibrated distance model using both the corrected $F^*$ values as
  well as the uncorrected $F$ brightness values.}
  \label{fig:calibrated}
\end{figure}

\section{Disagreement with existing research}

Previous studies use $F$ instead of $F*$. According to \citet{betoule2014},

\begin{displayquote}
  Specifically, the distance estimator used in this analysis (and in most
  similar cosmological analyses) assumes that supernovae with identical color,
  shape and galactic environment have on average the same intrinsic luminosity
  for all redshifts. This hypothesis is quantified by a linear model, yielding
  a standardized distance modulus $\mu = 5 \log_{10}{(d_L / 10 \text{pc})}$:

  \begin{equation}
  \label{eq:betoule_distance_modulus}
    \mu = m_B^* - (M_B - \alpha \times X_1 + \beta \times C)
  \end{equation}

  where $m_B^*$ corresponds to the observed peak magnitude in restframe $B$
  band and $\alpha$, $\beta$ and $M_B$ are nuisance parameters in the distance
  estimate.
\end{displayquote}

This statement may refer to the idea that a Type Ia supernova can have an
evolving intrinsic luminosity $L$ over time as conditions within the universe
change which was first hypothesized by \citet{tinsley1968}. In Equation
\ref{eq:betoule_distance_modulus}, there is no correction for redshift, which
suggests the interpretation that the flux $F$ is unaffected by redshift.

The model where $F$ is not corrected for redshift is explored in Figure
\ref{fig_uncorrected_uncalibrated} by replacing $F^*$ with $F$ in Equation
\ref{eq:D*} and obtaining

\begin{equation}
  D_L = k 10^\frac{M}{5}.
\end{equation}

\section{Conclusions}
\label{sec:conclusions}
